MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
change metagenomics to microbiome analysis

During the past decade, metagenomics data analysis is growing
exponentially. Some of the reasons behind this are the increasing
throughput of massively parallel sequencing technologies (with the
derived decrease in sequencing costs), and the wide impact of
metagenomics studies \citep{oulas2015metagenomics}, especially in human
health (diagnostics, treatments, drug response or prevention)
\citep{bikel2015combining}. We should also mention what could be called
the microbiome explosion: all kind of microbiomes (gut, mouth, skin,
urinary tract, airway, milk, bladder) are now routinely sequenced in
different conditions of health and disease, or after different
treatments. The impact of Metagenomics is also being felt in
environmental sciences \citep{ufarte2015discovery}, crop sciences, the
agrifood sector \citep{coughlan2015biotechnological}, bioenergy
\citep{yang2016discovery}, and biotechnology in general
\citep{cowan2015metagenomics} \citep{kodzius2015marine}. These new
possibilities for exploring the diversity of micro-organisms in the most
varied environments are opening new research areas, and drastically
changing the existing ones.

>>>>

During the past decade, metagenomics data analysis is growing
exponentially. Some of the reasons behind this are the increasing
throughput of massively parallel sequencing technologies (with the
derived decrease in sequencing costs), and the wide impact of
metagenomics studies \citep{oulas2015metagenomics}, especially in human
health (diagnostics, treatments, drug response or prevention)
\citep{bikel2015combining}. We should also mention what could be called
the microbiome explosion: all kind of microbiomes (gut, mouth, skin,
urinary tract, airway, milk, bladder) are now routinely sequenced in
different conditions of health and disease, or after different
treatments. The impact of microbiome analysis is also being felt in
environmental sciences \citep{ufarte2015discovery}, crop sciences, the
agrifood sector \citep{coughlan2015biotechnological}, bioenergy
\citep{yang2016discovery}, and biotechnology in general
\citep{cowan2015metagenomics} \citep{kodzius2015marine}. These new
possibilities for exploring the diversity of micro-organisms in the most
varied environments are opening new research areas, and drastically
changing the existing ones.
